Objective-First Design of Nanophotonic Waveguide Couplers

### 2011-10-14 presentations/ob1_wg_paper/opex_submission/paper.tex
Version that was submitted to OpEx.

For the design objective, we choose a boundary-value formulation
    based on $H_z^\text{perfect}$,
    where $H_z^\text{perfect}$ is constructed 
    of the exact input and output waveguide modes at the input and output ports
    of the optimization region (where the coupler will be placed),
    repectively, and of zero-amplitude fields at the unused ports,
    as illustrated in Fig.~\ref{fig:intro}.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{quickfig/intro} 
    \caption{Boundary-value formulation of the design objective.
        The values of $H_z^\text{perfect}$, 
            defined along the dashed box surrounding the design area
            (coupling structure), 
            are shown in orange (color online).
        The values of $H_z^\text{perfect}$ along the top and bottom edges
            of the dashed box are set to zero.
        In this schematic, the fundamental and second-order waveguide modes
            have been chosen as the input and output modes respectively.}
    \label{fig:intro}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{quickfig/fiber} 
    \caption{Coupler from a narrow, high-index ($\epsilon=12.25$) waveguide to
        a wide, low-index ($\epsilon=2.25$) waveguide. 
        On the left, the dielectric structure of the coupler 
        and surrounding input and output waveguides are shown.
        The $H_z^\text{perfect}$ boundary values used as 
        the design objective are plotted on the left as well
        (top and bottom boundary values were set to zero).
        On the right, we show the simulation results used
        to compute the performance of the device.
        The coupler converts $96.3\%$ of the input power to the
        designated output mode.
        The device is also extremely compact, 
        convering only $36 \times 66$ grid points,
        where the vacuum wavelength is 42 grid points.
        Computation time was 20 minutes on a personal computer.}
    \label{fig:fiber}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{quickfig/mode-conv} 
    \caption{Coupler that converts the fundamental waveguide mode to the
        second-order waveguide mode
        (a movie of the design progress is included as a
        supplementary material).
        This problem is quite difficult since the two modes are of 
        opposite symmetry.
        For example, adiabatic approaches cannot be applied to this case.
        However, our method produces a device 
        (which has the same dimensions and vacuum wavelength as Fig. 1) 
        with a coupling efficiency of $95.5\%$. 
        Computation time was 20 minutes on a personal computer.
        }
    \label{fig:mode}
    \end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{quickfig/air-core}
    \caption{Coupler between a dielectric slab waveguide to 
        an air-core waveguide.
        Here, not only are the modes of opposite symmetry,
        but the output waveguide operates on a fundamentally different
        principle (distributed reflection) than the input waveguide 
        (index guided).
        The device still achieves an efficiency of $83.3\%$, demonstrating the
        versatility of our method.
        The vacuum wavelength is 25 grid points, 
        while the device footprint is still $36 \times 66$ grid points.
        Computation time was 20 minutes on a personal computer.
        }
        \label{fig:aircore}
\end{figure}

>>>>

For the design objective, we choose a boundary-value formulation
    based on $H_z^\text{perfect}$,
    where $H_z^\text{perfect}$ is constructed 
    of the exact input and output waveguide modes at the input and output ports
    of the optimization region (where the coupler will be placed),
    repectively, and of zero-amplitude fields at the unused ports.

% \begin{figure}[htbp]
%     \centering
%     \includegraphics[width=\textwidth]{intro} 
%     \caption{Boundary-value formulation of the design objective.
%         The values of $H_z^\text{perfect}$, 
%             defined along the dashed box surrounding the design area
%             (coupling structure), 
%             are shown in orange (color online).
%         The values of $H_z^\text{perfect}$ along the top and bottom edges
%             of the dashed box are set to zero.
%         In this schematic, the fundamental and second-order waveguide modes
%             have been chosen as the input and output modes respectively.}
%     \label{fig:intro}
% \end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{fiber} 
    \caption{Coupler from a narrow, high-index ($\epsilon=12.25$) waveguide to
        a wide, low-index ($\epsilon=2.25$) waveguide. 
        On the left, the dielectric structure of the coupler 
        and surrounding input and output waveguides are shown.
        The $H_z^\text{perfect}$ boundary values used as 
        the design objective are plotted on the left as well
        (top and bottom boundary values were set to zero).
        On the right, we show the simulation results used
        to compute the performance of the device.
        The coupler converts $96.3\%$ of the input power to the
        designated output mode.
        The device is also extremely compact, 
        convering only $36 \times 66$ grid points,
        where the vacuum wavelength is 42 grid points.
        Computation time was 20 minutes on a personal computer.}
    \label{fig:fiber}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{mode-conv} 
    \caption{Coupler that converts the fundamental waveguide mode to the
        second-order waveguide mode
        (a movie of the design progress is included as a
        supplementary material).
        This problem is quite difficult since the two modes are of 
        opposite symmetry.
        For example, adiabatic approaches cannot be applied to this case.
        However, our method produces a device 
        (which has the same dimensions and vacuum wavelength as Fig. 1) 
        with a coupling efficiency of $95.5\%$. 
        Computation time was 20 minutes on a personal computer.
        }
    \label{fig:mode}
    \end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{air-core}
    \caption{Coupler between a dielectric slab waveguide to 
        an air-core waveguide.
        Here, not only are the modes of opposite symmetry,
        but the output waveguide operates on a fundamentally different
        principle (distributed reflection) than the input waveguide 
        (index guided).
        The device still achieves an efficiency of $83.3\%$, demonstrating the
        versatility of our method.
        The vacuum wavelength is 25 grid points, 
        while the device footprint is still $36 \times 66$ grid points.
        Computation time was 20 minutes on a personal computer.
        }
        \label{fig:aircore}
\end{figure}
